### 2019-08-10 chapters/3-background.tex
Add todo about declaration files
Finish Wrapper Objects
Add examples for generation of declaration files

\subsection{TypeCoercion}
\todo{Hablar de WTFS}
\todo{Aca incluir texto de what does it mean to be a JS Type}
\subsection{NPM Packages}
\todo{Agregar info de NPM by numbers! Cuantos downloads, cuantos packages, etc.}
\todo{https://snyk.io/blog/npm-passes-the-1-millionth-package-milestone-what-can-we-learn/}

\section{TypeScript}
\subsection{Declaration Files} \label{sec:declaration-files-background}
\subsection{Definitely Typedd}

>>>>

\subsection{TypeCoercion} \label{sec:background-js-type-coercion}
\todo{Hablar de WTFS}
\todo{Aca incluir texto de what does it mean to be a JS Type}
\subsection{NPM Packages} \label{sec:background-npm-packages}
\todo{Agregar info de NPM by numbers! Cuantos downloads, cuantos packages, etc.}
\todo{https://snyk.io/blog/npm-passes-the-1-millionth-package-milestone-what-can-we-learn/}

\todo{Agregar info de cómo se resuelve el modulo y dónde se busca, etc -> Mirar link Requiring modules in Node.js: Everything you need to know}

\section{TypeScript}
\subsection{Declaration Files} \label{sec:declaration-files-background}
\todo{Hablar de los tipos de declaration files que hay}
\subsection{Definitely Typedd}

### 2019-08-10 chapters/4-approach.tex
Add examples for generation of declaration files

\subsection{Output Format}
\todo{Explicar que es un JSON con todas las interactions. Explicar estructura de cómo se forma el JSON}

\subsection{Blacklisted Modules}
\input{figures/approach/blacklisted-modules/blacklistedModules.tex}
\todo{Incluir grafico con los blacklisted modules}

\subsection{Implementation}
\todo{NodeJS \& Docker. Mostrar cómo se invoca, etc.}

\section{TypeScript Declaration File Generation}
\todo{Tres tipos de modulos en TypeScript}
\todo{Traceids y que las signatures de las funciones no se unen, sino que se acumulan segun traceId. Obviamente las iguales no se escriben de vuelta.}
\todo{El nombre de las interfaces se crea con el nombre de la variable}
\todo{El tipo se extrae del valor en runtime.}
\subsection{Overloading} \label{sec:typescript-overloading}
\subsection{Implementation}
\todo{TypeScript \& Docker. Mostrar cómo se invoca, etc.}

>>>>

\subsection{Output}
Information is stored in a map containing \mintinline{bash}{FunctionContainer} entries. When the executions stops, Jalangi's callback \mintinline{bash}{endExecution()} is called and the information is saved as a JSON to a file.

\subsection{Blacklisted Modules}
When instrumenting a JS Library, Jalangi will try to instrument all required modules by resolving and finding the modules. Unfortunately, Jalangi's native behaviour is to stop the complete analysis if there is an error in the instrumentation of any of the required modules or in the script itself.

The workaround introduced by the implementation modifies Jalangi's behaviour for failing instrumentation. For a given required module, it first tries to instrument it. If the instrumentation if unsuccesful, it simply skips the instrumentation and returns the original uninstrumented module.

As expected, no Jalangi callbacks will be triggered for that module's code. However, this workaround enables to at least still get run-time information of other required modules by not breaking the complete analysis. As explained in \figref{fig:blacklisted-modules}, instead of stopping the analysis, failing modules are skipped but modules required by them do get instrumented anyway. Modifying Jalangi's instrumentation algorithm is out of the scope of this work.

The application can be invoked by passing an optional argument with the path to a a JSON file containing the list of modules that should not be instrumented.

\input{figures/approach/blacklisted-modules/blacklistedModules.tex}

\section{TypeScript Declaration File Generation}
The actual generation of the declaration file is the next step in the pipeline after gathering the run-time information, as shown in \figref{fig:tsd_generation_method_block_diagram}. It uses the JSON output file containing the run-time information and generates a TypeScript declaration file.

\input{figures/approach/typescript-declaration-files-generation-method/examples/generation-declaration-file.tex}

\input{figures/approach/typescript-declaration-files-generation-method/examples/generation-declaration-file-with-interfaces.tex}

TypeScript provides templates 
\todo{Tres tipos de modulos en TypeScript}
\todo{Traceids y que las signatures de las funciones no se unen, sino que se acumulan segun traceId. Obviamente las iguales no se escriben de vuelta.}
\todo{El nombre de las interfaces se crea con el nombre de la variable}
\todo{El tipo se extrae del valor en runtime.}
\subsection{Overloading} \label{sec:typescript-overloading}
\subsection{Type inference}
\subsection{Implementation}
\todo{TypeScript \& Docker. Mostrar cómo se invoca, etc.}

### 2019-08-10 figures/approach/typescript-declaration-files-generation-method/examples/generation-declaration-file-with-interfaces.tex
Add examples for generation of declaration files

\begin{figure}[h]
	\centering
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.48\textwidth}
			\jscode{code/typescript-declaration-file-generation/example-with-interfaces/index.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.js - Entry point to be executed with \mintinline{bash}{node index.js}]{\usebox{\mintedbox}}
	\hfill
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.5\textwidth}
			\jscode{code/typescript-declaration-file-generation/example-with-interfaces/printer.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[printer.js - Module for which the TS Declaration File is going to be generated]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.8\textwidth}
			\tscode{code/typescript-declaration-file-generation/example-with-interfaces/printer.d.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[printer/index.d.ts]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.7\textwidth}
			\tscode{code/typescript-declaration-file-generation/example-with-interfaces/index.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.ts]{\usebox{\mintedbox}}

	\subfloat{\includegraphics[width=1\textwidth]{figures/approach/typescript-declaration-files-generation-method/examples/example-with-interfaces/code-intelligence-vscode.png}}

	\caption[Declaration file generation example]{\textbf{Declaration file generation example} - Declaration file for the \mintinline{bash}{calculator} module is generated using the \mintinline{bash}{module-class.d.ts} template. Declaration file can be used within a TypeScript project: code intelligence features work as expected and the generated JavaScript file after compilation can be correctly executed.}
	\label{fig:run-time-information-gathering-get-field}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.45\textwidth}
			\jscode{code/typescript-declaration-file-generation/example-with-interfaces/index.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.js - Entry point to be executed with \mintinline{bash}{node index.js}]{\usebox{\mintedbox}}
	\hfill
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.54\textwidth}
			\jscode{code/typescript-declaration-file-generation/example-with-interfaces/printer.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[printer.js - Module for which the TS Declaration File is going to be generated]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.51\textwidth}
			\tscode{code/typescript-declaration-file-generation/example-with-interfaces/printer.d.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[printer/index.d.ts]{\usebox{\mintedbox}}
	\hfill
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.48\textwidth}
			\tscode{code/typescript-declaration-file-generation/example-with-interfaces/index.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.ts]{\usebox{\mintedbox}}

	\caption[Interfaces inference]{\textbf{Interfaces inference} - Declaration file for the \mintinline{bash}{printer} module is generated using the \mintinline{bash}{module-function-d-ts} template. Interface of the input argument is generated correctly. The name of the interface is always generated as \mintinline{bash}{'I__ + argumentName'}, in this case \mintinline{bash}{I__input}.}
	\label{fig:run-time-information-gathering-get-field}
\end{figure}

### 2019-08-10 figures/approach/typescript-declaration-files-generation-method/examples/generation-declaration-file.tex
Add examples for generation of declaration files

\begin{figure}[h]
	\centering
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.48\textwidth}
			\jscode{code/typescript-declaration-file-generation/example-with-interfaces/index.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.js - Entry point to be executed with \mintinline{bash}{node index.js}]{\usebox{\mintedbox}}
	\hfill
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.5\textwidth}
			\jscode{code/typescript-declaration-file-generation/example-with-interfaces/printer.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[printer.js - Module for which the TS Declaration File is going to be generated]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.8\textwidth}
			\tscode{code/typescript-declaration-file-generation/example-with-interfaces/printer.d.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[printer/index.d.ts]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.7\textwidth}
			\tscode{code/typescript-declaration-file-generation/example-with-interfaces/index.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.ts]{\usebox{\mintedbox}}

	\subfloat{\includegraphics[width=1\textwidth]{figures/approach/typescript-declaration-files-generation-method/examples/example-with-interfaces/code-intelligence-vscode.png}}

	\caption[Declaration file generation example]{\textbf{Declaration file generation example} - Declaration file for the \mintinline{bash}{calculator} module is generated using the \mintinline{bash}{module-class.d.ts} template. Declaration file can be used within a TypeScript project: code intelligence features work as expected and the generated JavaScript file after compilation can be correctly executed.}
	\label{fig:run-time-information-gathering-get-field}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.48\textwidth}
			\jscode{code/typescript-declaration-file-generation/index.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.js - Entry point to be executed with \mintinline{bash}{node index.js}]{\usebox{\mintedbox}}
	\hfill
	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.5\textwidth}
			\jscode{code/typescript-declaration-file-generation/calculator.js}
		\end{minipage}
	\end{lrbox}
	\subfloat[calculator.js - Module for which the TS Declaration File is going to be generated]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.7\textwidth}
			\tscode{code/typescript-declaration-file-generation/calculator.d.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[calculator/index.d.ts]{\usebox{\mintedbox}}

	\begin{lrbox}{\mintedbox}
		\begin{minipage}{0.7\textwidth}
			\tscode{code/typescript-declaration-file-generation/index.ts}
		\end{minipage}
	\end{lrbox}
	\subfloat[index.ts]{\usebox{\mintedbox}}
	\caption[Declaration file generation example]{\textbf{Declaration file generation example} - Declaration file for the \mintinline{bash}{calculator} module is generated using the \mintinline{bash}{module-class.d.ts} template. Declaration file can be used within a TypeScript project: code intelligence features work as expected and the generated JavaScript file after compilation can be correctly executed.}
	\label{fig:run-time-information-gathering-get-field}
\end{figure}
